Supplementary Information -- Morphological convergence as on-line lexical analogy

### 2020-10-15 supplementary_information/si.Rnw
proof check

# libraries
library(tidyverse) # for data wrangling, figures
library(purrr) # for functional programming
library(stringr) # for string manipulation
library(readr) # for reading
library(scales) # for rescaling
library(xtable) # for latex tables
library(lme4) # for GLMM-s
library(broom) # for tidy summaries
library(ggthemes) # for colourblind scale

@@

# takes lmer fit, spits out coef table with ast
niceCoefTable = function(fit){
  my_table = fit %>% 
    tidy %>% 
    filter(
      group == 'fixed'
    ) %>% 
    mutate(
      sig = case_when(
        p.value >= 0.05 ~ 'n.s.',
        p.value < 0.05 & p.value >= 0.01 ~ '*',
        p.value < 0.01 & p.value >= 0.001 ~ '**',
        p.value < 0.001 ~ '***'
      )
    ) %>%
    rename(`Z score` = statistic) %>% 
    select(
      - p.value,
      - group
    )
return(my_table)  
}

@@

This is an Sweave file. The Rnw source file contains the code used to compile the pdf output file. It also contains additional code sections that help replicate the results. The file also contains pointers to further detail in the supplementary repository that accompanies the paper.

@@

# here are the effect estimate figures from the paper:
# plot(effects::effect('co_player_regularisation_rate', lme.fit1), xlab = 'co-player regularization shift', ylab = 'player post-test regularization', main = 'Effect of co-player rate of regularization on pos-test responses')

# plot(effects::effect('verb_baseline_average:co_player_lexical_typicality', lme.fit1), multiline = T, lines=list(lty=c(1,2,3)), xlab = 'verb baseline average', ylab = 'player post-test regularization', main = 'Effect of co-player lexical typicality on pos-test responses')

@@

<<main_model3, echo=F,eval=T, results=tex>>=
load('models/si_fit1.rda')
lme.fit1.sum = niceCoefTable(lme.fit1)

>>>>

# libraries
library(tidyverse) # for data wrangling, figures
library(purrr) # for functional programming
library(stringr) # for string manipulation
library(readr) # for reading
library(scales) # for rescaling
library(xtable) # for latex tables
library(lme4) # for GLMM-s
library(broom) # for tidy summaries
library(broom.mixed) # for tidy summaries, lmer
library(ggthemes) # for colourblind scale

@@

# takes lmer fit, spits out coef table with ast
niceCoefTable = function(fit){
  my_table = fit %>% 
    tidy %>% 
    dplyr::filter(
      effect == 'fixed'
    ) %>% 
    dplyr::mutate(
      sig = case_when(
        p.value >= 0.05 ~ 'n.s.',
        p.value < 0.05 & p.value >= 0.01 ~ '*',
        p.value < 0.01 & p.value >= 0.001 ~ '**',
        p.value < 0.001 ~ '***'
      )
    ) %>%
    dplyr::rename(`Z score` = statistic) %>% 
    select(
      - effect,
      - p.value,
      - group
    )
return(my_table)  
}

@@

The source file for this SI, along with the data and the code for the paper, are hosted at https://github.com/petyaracz/RaczHayPierrehumbert2019.
% This is an Sweave file. The Rnw source file contains the code used to compile the pdf output file. It also contains additional code sections that help replicate the results. The file also contains pointers to further detail in the supplementary repository that accompanies the paper.

@@

# here are the effect estimate figures from the paper:
plot(effects::effect('co_player_regularisation_rate', lme.fit1), xlab = 'co-player regularization shift', ylab = 'player post-test regularization', main = 'Effect of co-player rate of regularization on post-test responses', lwd = 2)

plot(effects::effect('verb_baseline_average:co_player_lexical_typicality', lme.fit1), multiline = T, lines=list(lty=c(1,2,3)), lwd = 2, xlab = 'verb baseline average', ylab = 'player post-test regularization', main = 'Effect of co-player lexical typicality on post-test responses')

@@

<<main_model3, echo=F,eval=T, results=tex>>=
load('~/Github/RaczBecknerHayPierrehumbert2019/supplementary_information/models/si_fit1.rda')
lme.fit1.sum = niceCoefTable(lme.fit1)

### 2020-10-15 supplementary_information/si.tex
na
proof check

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:26 2020
\begin{table}[ht]
\centering
\begin{tabular}{llll}
  \hline
verb class & irregular set & regular set & miscellaneous regular verbs \\ 
  \hline
BURNT & 6 & 42 & 1218 \\ 
  DROVE & 14 & 83 & 1218 \\ 
  KEPT & 12 & 31 & 1218 \\ 
  SANG & 8 & 13 & 1218 \\ 
  count of unique forms & 40 & 169 & 1218 \\ 
   \hline
\end{tabular}
\caption{Number of forms in each verb class, GCM training data} 
\label{gcmsetsize}
\end{table}
\subsection{Estimation}

To calculate the similarity between two words, we first compute their dissimilarity. This is achieved using the string-edit (Levenshtein) distance, which is the smallest number of changes needed to transform one word into the other. Costs range from 0 (the corresponding segments are identical) to 1 (inserting or deleting an entire segment). Following \cite{albright2003rules} and \cite{dawdy2014learnability}, costs between 0 and 1 are assigned to corresponding segments that are not identical, based on how much the segments differ.

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:26 2020
\begin{table}[ht]
\centering
\begin{tabular}{llrr}
  \hline
category & rule.type & related forms & exceptions \\ 
  \hline
BURNT & irregular &  24 &  41 \\ 
  DROVE & irregular &  21 & 114 \\ 
  KEPT & irregular &  10 &   9 \\ 
  SANG & irregular &  11 &  77 \\ 
  BURNT & regular &  38 &  21 \\ 
  DROVE & regular &  29 &  27 \\ 
  KEPT & regular &  67 &  41 \\ 
  SANG & regular &  47 &  38 \\ 
   \hline
\end{tabular}
\caption{Number of forms in each verb class, MGL training data} 
\label{mglsetsize}
\end{table}
\subsection{Estimation}

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:26 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
  \hline
category & irregular rule & regular rule & sum \\ 
  \hline
burnt &   4 &   2 &   6 \\ 
  drove &  13 &   3 &  16 \\ 
  kept &   5 &   5 &  10 \\ 
  sang &  10 &   4 &  14 \\ 
   \hline
\end{tabular}
\caption{Number of regular and irregular rules in each verb class, posited by the MGL for the training data (Note that the regular rules themselves overlap)} 
\label{mglruletable}
\end{table}

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:26 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -0.11 & 0.16 & -0.67 & n.s. \\ 
  verb\_baseline\_average & 8.26 & 0.69 & 12.04 & *** \\ 
  co\_player\_lexical\_typicalityrandom & 0.04 & 0.17 & 0.25 & n.s. \\ 
  co\_player\_lexical\_typicalityreversed & 0.04 & 0.17 & 0.20 & n.s. \\ 
  participant\_prereg\_average & 7.13 & 0.56 & 12.67 & *** \\ 
  co\_player\_regularisation\_rate-40\% & -0.46 & 0.18 & -2.47 & * \\ 
  co\_player\_regularisation\_rate+40\% & 0.55 & 0.17 & 3.31 & *** \\ 
  verb\_baseline\_average:co\_player\_lexical\_typicalityrandom & -2.40 & 0.93 & -2.59 & ** \\ 
  verb\_baseline\_average:co\_player\_lexical\_typicalityreversed & -2.13 & 0.96 & -2.23 & * \\ 
   \hline
\end{tabular}
\caption{Experimental Data, Post-test Regression Model Summary. Model formula: post-test regular response ~ verb baseline mean x lexical typicality + participant pretest mean + regularization shift + (1 + verb.baseline.mean | participant) + (1 | verb)} 
\label{regressiontable1}
\end{table}
In the model in Table 5 in the main text, repeated here as Table \ref{regressiontable1}, we elect to mean center continuous variables to counteract collinearity that becomes evident when including the interaction between {\em verb baseline average} and {\em lexical typicality}.  Although some debate exists regarding the practice of transforming variables \citep{belsley1991conditioning,echambadi2007mean}, centering variables is common practice to remove nonessential ill conditioning, that is, relationships that inevitably exist between main and product terms \citep{aiken1991multiple,jaccard2003interaction, jaeger2008categorical}. We note that if {\em verb baseline mean} is {\em not} centered, collinearity is high (VIF=15.79) in this model. A non-centered model also yields a significant main effect for {\em lexical typicality}, with increased post-test regularization in the random and reversed conditions. However, we elect to take a more conservative approach by not including a potentially spurious main effect. Note that other than this main effect difference, models with and without centering yield results that are qualitatively indistinguishable; all other main effects and interactions are present in either case. The collinearity for the centered model (Table 5 in the main text) is acceptable, with a maximum VIF score of 2.9.

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:27 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -0.53 & 0.12 & -4.22 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.35 & 0.09 & 14.48 & *** \\ 
  rescaled\_CELEX\_gcm\_feature\_distance\_residual & 1.42 & 0.13 & 11.10 & *** \\ 
   \hline
\end{tabular}
\caption{Model 3: MGL scores and GCM residuals, baseline data} 
\label{resid1}
\end{table}
% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:27 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -1.23 & 0.16 & -7.68 & *** \\ 
  rescaled\_CELEX\_gcm\_feature\_distance & 2.39 & 0.15 & 16.06 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance\_residual & 1.01 & 0.09 & 11.15 & *** \\ 
   \hline
\end{tabular}
\caption{Model 4: GCM scores and MGL residuals, baseline data} 
\label{resid2}
\end{table}
Model 1 predicts the GCM scores from the MGL scores (M1: GCM regular score  $\sim$ MGL regular score). Model 2 predicts the MGL scores from the GCM scores (M2: MGL regular score  $\sim$ GCM regular score). In two additional models, we then use the residuals from each model (M1, M2) as an estimate of the variation present in one score that cannot be attributed to the other.  First, we use the residuals of Model 1 in another, mixed-effects logistic regression model along with the MGL scores to predict regular responses in the baseline task (M3: regular response  $\sim$ MGL score + GCM residual + (1 + MGL score + GCM residual$|$participant) + (1 $|$ verb)). We then residualize for the MGL. We use the residuals of Model 2 along with the GCM scores in a similar logistic regression model (M4: regular response  $\sim$ GCM score + MGL residual + (1 + GCM score + MGL residual $|$participant)).

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:27 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -2.95 & 0.29 & -10.01 & *** \\ 
  rescaled\_CELEX\_gcm\_feature\_distance & 4.37 & 0.42 & 10.28 & *** \\ 
  gcm\_score\_diff & 2.61 & 0.47 & 5.56 & *** \\ 
  participant\_prereg\_average & 5.29 & 0.60 & 8.79 & *** \\ 
   \hline
\end{tabular}
\caption{Model 5: Celex-GCM and individual score difference, post-test data} 
\label{indiv1}
\end{table}
% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:27 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -1.32 & 0.15 & -8.66 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.94 & 0.18 & 11.04 & *** \\ 
  mgl\_score\_diff & 0.30 & 0.14 & 2.18 & * \\ 
  participant\_prereg\_average & 7.20 & 0.59 & 12.19 & *** \\ 
   \hline
\end{tabular}
\caption{Model 6: Celex-MGL and individual score difference, post-test data} 
\label{indiv2}
\end{table}
We do this for both the GCM  (Model 5: regular response  $\sim$ \textsc{Celex} GCM score + extra GCM information + participant pre-test mean + (1 + \textsc{Celex} GCM + extra GCM information$|$participant) + (1$|$verb) and the MGL (Model 6: regular response  $\sim$ \textsc{Celex} MGL score + extra MGL information + participant pre-test mean + (1 + \textsc{Celex} MGL + extra MGL information$|$participant)+ (1$|$verb)).

@@

% latex table generated in R 3.6.0 by xtable 1.8-4 package
% Mon Apr 20 20:04:28 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & statistic & sig \\ 
  \hline
(Intercept) & -2.94 & 0.27 & -10.90 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.60 & 0.17 & 9.36 & *** \\ 
  rescaled\_individual\_gcm\_feature\_distance & 2.79 & 0.38 & 7.37 & *** \\ 
  participant\_prereg\_average & 5.44 & 0.58 & 9.30 & *** \\ 
   \hline
\end{tabular}
\caption{Celex-MGL and Individual-GCM predict variation in the post-test} 
\label{comp3}
\end{table}
Goodness-of-fit tests show that model fit is significantly worse if we exclude {\sc Celex}-MGL ($\chi^2 = $ 201.86 ***) or individual-GCM ($\chi^2 = $ 81.82 ***) as predictors. It is not significantly better if we include individual-MGL ($\chi^2 = $ 0.09, p = 0.77) or {\sc Celex}-GCM ($\chi^2 = $ 2.03, p = 0.15).

>>>>

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Oct 15 15:19:32 2020
\begin{table}[ht]
\centering
\begin{tabular}{llll}
  \hline
verb class & irregular set & regular set & miscellaneous regular verbs \\ 
  \hline
BURNT & 6 & 42 & 1218 \\ 
  DROVE & 14 & 83 & 1218 \\ 
  KEPT & 12 & 31 & 1218 \\ 
  SANG & 8 & 13 & 1218 \\ 
  count of unique forms & 40 & 169 & 1218 \\ 
   \hline
\end{tabular}
\caption{Number of forms in each verb class, GCM training data} 
\label{gcmsetsize}
\end{table}
\subsection{Estimation}

To calculate the similarity between two words, we first compute their dissimilarity. This is achieved using the string-edit (Levenshtein) distance, which is the smallest number of changes needed to transform one word into the other. For one unit of edit distance, these costs range from 0 (the corresponding segments are identical) to 1 (inserting or deleting an entire segment). Following \cite{albright2003rules} and \cite{dawdy2014learnability}, costs between 0 and 1 are assigned to corresponding segments that are not identical, based on how much the segments differ.

@@

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Oct 15 15:19:33 2020
\begin{table}[ht]
\centering
\begin{tabular}{llrr}
  \hline
category & rule.type & related forms & exceptions \\ 
  \hline
BURNT & irregular &  24 &  41 \\ 
  DROVE & irregular &  21 & 114 \\ 
  KEPT & irregular &  10 &   9 \\ 
  SANG & irregular &  11 &  77 \\ 
  BURNT & regular &  38 &  21 \\ 
  DROVE & regular &  29 &  27 \\ 
  KEPT & regular &  67 &  41 \\ 
  SANG & regular &  47 &  38 \\ 
   \hline
\end{tabular}
\caption{Number of forms in each verb class, MGL training data} 
\label{mglsetsize}
\end{table}
\subsection{Estimation}

@@

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Oct 15 15:19:33 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
  \hline
category & irregular rule & regular rule & sum \\ 
  \hline
burnt &   4 &   2 &   6 \\ 
  drove &  13 &   3 &  16 \\ 
  kept &   5 &   5 &  10 \\ 
  sang &  10 &   4 &  14 \\ 
   \hline
\end{tabular}
\caption{Number of regular and irregular rules in each verb class, posited by the MGL for the training data (Note that the regular rules themselves overlap)} 
\label{mglruletable}
\end{table}

@@

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Oct 15 15:19:33 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & Z score & sig \\ 
  \hline
(Intercept) & -0.11 & 0.16 & -0.67 & n.s. \\ 
  verb\_baseline\_average & 8.26 & 0.69 & 12.04 & *** \\ 
  co\_player\_lexical\_typicalityrandom & 0.04 & 0.17 & 0.25 & n.s. \\ 
  co\_player\_lexical\_typicalityreversed & 0.04 & 0.17 & 0.20 & n.s. \\ 
  participant\_prereg\_average & 7.13 & 0.56 & 12.67 & *** \\ 
  co\_player\_regularisation\_rate-40\% & -0.46 & 0.18 & -2.47 & * \\ 
  co\_player\_regularisation\_rate+40\% & 0.55 & 0.17 & 3.31 & *** \\ 
  verb\_baseline\_average:co\_player\_lexical\_typicalityrandom & -2.40 & 0.93 & -2.59 & ** \\ 
  verb\_baseline\_average:co\_player\_lexical\_typicalityreversed & -2.13 & 0.96 & -2.23 & * \\ 
   \hline
\end{tabular}
\caption{Experimental Data, Post-test Regression Model Summary. Model formula: post-test regular response ~ verb baseline mean x lexical typicality + participant pretest mean + regularization shift + (1 + verb.baseline.mean | participant) + (1 | verb)} 
\label{regressiontable1}
\end{table}
In the model in Table 5 in the main text, repeated here as Table \ref{regressiontable1}, we elect to mean center continuous variables to counteract collinearity that becomes evident when including the interaction between {\em verb baseline average} and {\em lexical typicality}.  Although some debate exists regarding the practice of transforming variables \citep{belsley1991conditioning,echambadi2007mean}, centering variables is common practice to remove nonessential ill conditioning, that is, relationships that inevitably exist between main and product terms \citep{aiken1991multiple,jaccard2003interaction, jaeger2008categorical}. We note that if {\em verb baseline mean} is {\em not} centered, collinearity is high (VIF=15.79) in this model. A non-centered model also yields a significant main effect for {\em lexical typicality}, with increased post-test regularization in the random and reversed conditions. However, we elect to take a more conservative approach by not including a potentially spurious main effect. Note that other than this main effect difference, models with and without centering yield results that are qualitatively indistinguishable; all other main effects and interactions are present in either case. The collinearity for the centered model (Table 5 in the main text) is acceptable, with a maximum VIF score of 2.9.

@@

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Oct 15 15:19:34 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & Z score & sig \\ 
  \hline
(Intercept) & -0.53 & 0.12 & -4.22 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.35 & 0.09 & 14.48 & *** \\ 
  rescaled\_CELEX\_gcm\_feature\_distance\_residual & 1.42 & 0.13 & 11.10 & *** \\ 
   \hline
\end{tabular}
\caption{Model 3: MGL scores and GCM residuals, baseline data} 
\label{resid1}
\end{table}
% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Oct 15 15:19:34 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & Z score & sig \\ 
  \hline
(Intercept) & -1.23 & 0.16 & -7.68 & *** \\ 
  rescaled\_CELEX\_gcm\_feature\_distance & 2.39 & 0.15 & 16.06 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance\_residual & 1.01 & 0.09 & 11.15 & *** \\ 
   \hline
\end{tabular}
\caption{Model 4: GCM scores and MGL residuals, baseline data} 
\label{resid2}
\end{table}
Model 1 predicts the GCM scores from the MGL scores (M1: GCM regular score  $\sim$ MGL regular score). Model 2 predicts the MGL scores from the GCM scores (M2: MGL regular score  $\sim$ GCM regular score). In two additional models, we then use the residuals from each model (M1, M2) as an estimate of the variation present in one score that cannot be attributed to the other.  First, we use the residuals of Model 1 in another, mixed-effects logistic regression model along with the MGL scores to predict regular responses in the baseline task (M3: regular response  $\sim$ MGL score + GCM residual + (1 + MGL score + GCM residual$|$participant) + (1 $|$ verb)). We then residualize for the MGL. We use the residuals of Model 2 along with the GCM scores in a similar logistic regression model (M4: regular response  $\sim$ GCM score + MGL residual + (1 + GCM score + MGL residual $|$participant)).

@@

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Oct 15 15:19:34 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & Z score & sig \\ 
  \hline
(Intercept) & -2.95 & 0.29 & -10.01 & *** \\ 
  rescaled\_CELEX\_gcm\_feature\_distance & 4.37 & 0.42 & 10.28 & *** \\ 
  gcm\_score\_diff & 2.61 & 0.47 & 5.56 & *** \\ 
  participant\_prereg\_average & 5.29 & 0.60 & 8.79 & *** \\ 
   \hline
\end{tabular}
\caption{Model 5: Celex-GCM and individual score difference, post-test data} 
\label{indiv1}
\end{table}
% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Oct 15 15:19:35 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & Z score & sig \\ 
  \hline
(Intercept) & -1.32 & 0.15 & -8.66 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.94 & 0.18 & 11.04 & *** \\ 
  mgl\_score\_diff & 0.30 & 0.14 & 2.18 & * \\ 
  participant\_prereg\_average & 7.20 & 0.59 & 12.19 & *** \\ 
   \hline
\end{tabular}
\caption{Model 6: Celex-MGL and individual score difference, post-test data} 
\label{indiv2}
\end{table}
We do this for both the GCM  (Model 5: regular response  $\sim$ \textsc{Celex} GCM score + extra GCM information + participant pre-test mean + (1 + \textsc{Celex} GCM + extra GCM information$|$participant) + (1$|$verb) and the MGL (Model 6: regular response  $\sim$ \textsc{Celex} MGL score + extra MGL information + participant pre-test mean + (1 + \textsc{Celex} MGL + extra MGL information$|$participant)+ (1$|$verb)).

@@

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Oct 15 15:19:35 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrl}
  \hline
term & estimate & std.error & Z score & sig \\ 
  \hline
(Intercept) & -2.94 & 0.27 & -10.90 & *** \\ 
  rescaled\_CELEX\_mgl\_feature\_distance & 1.60 & 0.17 & 9.36 & *** \\ 
  rescaled\_individual\_gcm\_feature\_distance & 2.79 & 0.38 & 7.37 & *** \\ 
  participant\_prereg\_average & 5.44 & 0.58 & 9.30 & *** \\ 
   \hline
\end{tabular}
\caption{Celex-MGL and Individual-GCM predict variation in the post-test} 
\label{comp3}
\end{table}
Goodness-of-fit tests show that model fit is significantly worse if we exclude {\sc Celex}-MGL ($\chi^2 = $ 201.86 ***) or individual-GCM ($\chi^2 = $ 81.82 ***) as predictors. It is not significantly better if we include individual-MGL ($\chi^2 = $ 0.09, p = 0.77) or {\sc Celex}-GCM ($\chi^2 = $ 2.03, p = 0.15).
